---
title: "Examine the Digital Clues"
subtitle: "Case file RUFFR-2113"
format:
  html:
    toc: true
    code-fold: false
execute:
  warning: false
  message: false
---

The five suspects admit that they returned to the university because they had procrastinated. Each claims to have been working somewhere else inside the building when the pipeline was damaged.

Examine the digital evidence and decide which alibis are supported.

::: {.callout-warning}
Remember

Logs identify accounts, devices, and access cards—not necessarily the dog physically using them.

A digital alibi is therefore **provisional**. Samples from all five dogs must still be examined in the laboratory.
:::


## Clue 1: The signed Git commit

Kommissar RegEx claims that he was reviewing another repository from a workstation in a different university room at 21:13.

Let’s inspect the Git records.

```{r}

kommissar_evidence <- git_log |>
  filter(
    user == "kommissar-regex",
    time >= as_hms("21:12:45"),
    time <= as_hms("21:13:15"),
    signature_valid
  )

```

<details class="clue-result">
<summary><strong>Reveal the finding</strong></summary>

```{r}

kommissar_evidence |>
  select(time, workstation, repository, message) |>
  kable(
    col.names = c(
      "Time",
      "Workstation",
      "Repository",
      "Commit"
    )
  )

```


A verified commit was made through Kommissar RegEx’s authenticated account at **21:13:04** from another university room.

That is a strong digital alibi—but is it perfect? Someone else might theoretically have used his authenticated session.

**Provisional digital alibi supported:** Kommissar RegEx

**Still lacking a digital alibi:** Sava Sniffer, Klara Cache, Lady Byte, and Vera Vector

**Laboratory status:** All five dogs remain under investigation.

</details>

## Clue 2: The active cache

Klara Cache claims that she was monitoring a long-running workflow in the reproducibility room.

Did her authenticated session remain active around 21:13?

```{r}
klara_evidence <- cache_events |>
  filter(
    user == "klara-cache",
    time >= as_hms("21:12:00"),
    time <= as_hms("21:14:00")
  ) |>
  arrange(time)

klara_before <- any(klara_evidence$time < incident_time)
klara_after  <- any(klara_evidence$time > incident_time)

klara_alibi_supported <- klara_before && klara_after

```

<details class="clue-result">
<summary><strong>Reveal the finding</strong></summary>

```{r}
klara_evidence |>
  select(time, workstation, event, target) |>
  kable(
    col.names = c(
      "Time",
      "Workstation",
      "Cache event",
      "Target"
    )
  )

```


Interesting! Klara’s authenticated workstation recorded cache activity immediately before and after the pipeline was damaged.

This supports her story. However, a cached process can run automatically, and an authenticated session could be used by another dog.

**Provisional digital alibi supported:** Klara Cache

**Digital alibis supported so far:** Kommissar RegEx and Klara Cache

**Still lacking a digital alibi:** Sava Sniffer, Lady Byte, and Vera Vector

**Laboratory status:** All five dogs remain under investigation.

</details>

## Clue 3: The missing semicolon

Sava Sniffer claims that he was following the scent of a missing semicolon through another repository.

Let’s search the server logs.

```{r}
sava_evidence <- server_log |>
  filter(
    user == "sava-sniffer",
    str_detect(
      message,
      regex("semicolon|;", ignore_case = TRUE)
    ),
    time >= as_hms("21:12:00"),
    time <= as_hms("21:14:00")
  ) |>
  arrange(time)

sava_before <- any(sava_evidence$time < incident_time)
sava_after  <- any(sava_evidence$time > incident_time)

sava_alibi_supported <- sava_before && sava_after
```

<details class="clue-result">
<summary><strong>Reveal the finding</strong></summary>

```{r}
sava_evidence |>
  select(time, repository, message) |>
  kable(
    col.names = c(
      "Time",
      "Repository",
      "Log message"
    )
  )
```

There it is! Sava’s authenticated account submitted commands immediately before and after 21:13 while searching the missing-semicolon repository.

This is another strong digital alibi—but it still identifies an account rather than conclusively identifying the paws at the keyboard.

**Provisional digital alibi supported:** Sava Sniffer

**Digital alibis supported:** Kommissar RegEx, Klara Cache, and Sava Sniffer

**Digital finalists:** Lady Byte and Vera Vector

**Laboratory status:** Samples from all five dogs must still be examined.

</details>

## Two digital finalists—but five laboratory samples

Three dogs have produced strong digital alibis:

- Kommissar RegEx
- Klara Cache
- Sava Sniffer

Lady Byte and Vera Vector remain the two **digital finalists**.

But wait—could another dog have used Kommissar’s authenticated session? Could Klara’s cache have continued automatically? Could someone have submitted commands through Sava’s account?

The digital evidence alone cannot answer those questions.

The laboratory must therefore compare the bite, hair, and paw samples from **all five dogs**.

[Send the evidence to the laboratory](lab.qmd){.btn .btn-warning .btn-lg}
