---
title: "Paw & Order: The Broken Pipe Unit"
---

The international RuffR Data Science Conference is taking place at Campus Gotland in Visby. At 02:13, the conference’s R pipeline suddenly stops working. Someone has chewed the > from the native pipe operator:

suspects |
  filter(has_alibi == FALSE)

Twenty-five dogs are attending the conference, but only five members of the overnight Pipeline Response Team had access to the restricted project room.

The player must examine the evidence, test the suspects’ alibis and identify who broke the R code.

The suspects
Sava Sniffer — a Serbian Hound from Serbia
Klara Cache — a Karst Shepherd Dog from Slovenia
Byte Biter — a Chihuahua from Mexico
Kommissar RegEx — a German Shepherd Dog with German–Austrian citizenship
Vera Vector — a Swedish Vallhund from Sweden

Each suspect has a different programming speciality, travel history and explanation for their whereabouts at the time of the crime.

Gameplay

The investigation progresses through several stages:

Explore an interactive map showing the suspects’ journeys to Visby.
Meet the five suspects and learn about their breeds and conference roles.
Examine evidence from Git, the targets cache and server logs.
Reveal clue results to eliminate innocent suspects.
Analyse simulated bite-mark, hair and paw-print evidence.

```{r}
install.packages(c("leaflet", "rnaturalearth", "rnaturalearthdata", "sf", "dplyr"))
```


---
title: "Dog Origins"
---

```{r}
#| label: setup
#| message: false

library(dplyr)
library(sf)
library(rnaturalearth)
library(leaflet)
```

```{r}
---
title: "Dog Origins"
---

```{r}
#| label: setup
#| message: false

library(dplyr)
library(sf)
library(rnaturalearth)
library(leaflet)
```

```{r}
#| label: map
#| echo: false
#| warning: false

world <- ne_countries(scale = "medium", returnclass = "sf")

# Get centroid coordinates for each country
centroids <- world |>
  st_centroid() |>
  st_coordinates() |>
  as.data.frame() |>
  mutate(name = world$name)

# Join dog data to centroids by country name
dog_map <- data |>
  left_join(centroids, by = c("Origin" = "name"))

leaflet(dog_map) |>
  addTiles() |>
  addMarkers(
    lng = ~X, lat = ~Y,
    popup = ~paste0(
      "<b>", Name, "</b><br>",
      "Breed: ", `Dog Breed`, "<br>",
      "Origin: ", Origin, "<br>",
      "Hair Color: ", `Hair Color`, "<br>",
      "Hair Length: ", `Hair Length (cm)`, " cm<br>",
      "Bite Size: ", `Bite Size / Jaw Width (cm)`, " cm"
    ),
    label = ~Name
  )

```