---
title: "Paw & Order: The Broken Pipe Unit"
---

The international RuffR Data Science Conference is taking place at Campus Gotland in Visby. At 02:13, the conference’s R pipeline suddenly stops working. Someone has chewed the > from the native pipe operator:

```{r}
#| eval: false
suspects |
  filter(has_alibi == FALSE)
```

Twenty-five dogs are attending the conference, but only five members of the overnight Pipeline Response Team had access to the restricted project room.

Pipeline Response Team
Sava Sniffer — a Serbian Hound from Serbia
Klara Cache — a Karst Shepherd Dog from Slovenia
Byte Biter — a Chihuahua from Mexico
Kommissar RegEx — a German Shepherd Dog with German–Austrian citizenship
Vera Vector — a Swedish Vallhund from Sweden

Each suspect has a different programming speciality, travel history and explanation for their whereabouts at the time of the crime.

```{r}
#| label: install-packages
#| echo: false

#install.packages(c("leaflet", "rnaturalearth", "rnaturalearthdata", "sf", "dplyr"))
```

```{r}
#| label: setup
#| message: false
#| echo: false

library(tidyverse)
library(sf)
library(rnaturalearth)
library(leaflet)
library(here)
```

```{r}
#| label: load-data
#| echo: false

data <- read_csv("data/dog_database.csv")
```


```{r}
#| label: map
#| echo: false
#| warning: false

world <- ne_countries(scale = "medium", returnclass = "sf")

centroids <- world |>
  st_centroid() |>
  st_coordinates() |>
  as.data.frame() |>
  mutate(name = world$name)

dog_map <- data |>
  left_join(centroids, by = c("Origin" = "name")) |>
  mutate(img_path = paste0("test_dog_images/", Name, ".jpg"))  # adjust extension/pattern as needed

# Custom icon: use each dog's photo as the marker, small thumbnail size
dog_icons <- icons(
  iconUrl = dog_map$img_path,
  iconWidth = 100, iconHeight = 100,
  className = "dog-marker-icon"
)

leaflet(dog_map) |>
  addTiles() |>
  addMarkers(
    lng = ~X, lat = ~Y,
    icon = dog_icons,
    popup = ~paste0(
      "<b>", Name, "</b><br>",
      "<img src='", img_path, "' width='150'><br>",
      "Breed: ", `Dog Breed`, "<br>",
      "Origin: ", Origin, "<br>",
      "Hair Color: ", `Hair Color`, "<br>",
      "Hair Length: ", `Hair Length (cm)`, " cm<br>",
      "Bite Size: ", `Bite Size / Jaw Width (cm)`, " cm"
    ),
    label = ~Name
  )
```

```{css}
/*| echo: false */
.dog-marker-icon {
  border-radius: 50%;
  border: 2px solid white;
  box-shadow: 0 0 4px rgba(0,0,0,0.5);
}
```
