---
title: "Paw & Order: The Broken Pipe Unit"
---

The international RuffR Data Science Conference is taking place at Campus Gotland in Visby. At 02:13, the conference’s R pipeline suddenly stops working. Someone has chewed the > from the native pipe operator:

```{r}
#| eval: false
suspects |
  filter(has_alibi == FALSE)
```

Twenty-five dogs are attending the conference, but only five members of the overnight Pipeline Response Team had access to the restricted project room. They quickly became the only suspects.

Pipeline Response Team

- Sava Sniffer — a Serbian Hound from Serbia
- Klara Cache — a Karst Shepherd Dog from Slovenia
- Byte Biter — a Chihuahua from Mexico
- Kommissar RegEx — a German Shepherd Dog with German–Austrian citizenship
- Vera Vector — a Swedish Vallhund from Sweden

Each suspect has a different programming speciality, travel history and explanation for their whereabouts at the time of the crime. 

Check out their details by hovering on the images or in the [Suspects](suspects/dog_index.qmd) tab.

```{r}
#| label: install-packages
#| echo: false

#install.packages(c("leaflet", "rnaturalearth", "rnaturalearthdata", "sf", "dplyr", "shinyLive"))
```

```{r}
#| label: setup
#| message: false
#| echo: false
#| warning: false

library(tidyverse)
library(sf)
library(rnaturalearth)
library(leaflet)
library(here)
```

```{r}
#| label: load-data
#| echo: false
#| message: false

data <- read_csv("data/dog_database.csv")
```


```{r}
#| label: map
#| echo: false
#| warning: false
#| message: false

world <- ne_countries(scale = "medium", returnclass = "sf")

centroids <- world |>
  st_centroid() |>
  st_coordinates() |>
  as.data.frame() |>
  mutate(name = world$name)

#dog_map <- data |>
  #left_join(centroids, by = c("Origin" = "name")) |>
  #mutate(img_path = paste0("dog_portraits/", Name, ".jpg"))  # adjust extension/#pattern as needed

dog_map <- data |>
  left_join(centroids, by = c("Origin" = "name")) |>
  rowwise() |>
  mutate(
    img_path = {
      name_prefix <- str_sub(Name, 1, 4)  # first 4 letters, e.g. "Sava"
      matched_file <- list.files("dog_portraits", pattern = name_prefix, full.names = TRUE)
      if (length(matched_file) > 0) matched_file[1] else NA_character_
    }
  ) |>
  ungroup()

# Custom icon: use each dog's photo as the marker, small thumbnail size
dog_icons <- icons(
  iconUrl = dog_map$img_path,
  iconWidth = 100, iconHeight = 100,
  className = "dog-marker-icon"
)

leaflet(dog_map) |>
  addTiles() |>
  addMarkers(
    lng = ~X, lat = ~Y,
    icon = dog_icons,
    popup = ~paste0(
      "<b>", Name, "</b><br>",
      "<img src='", img_path, "' width='150'><br>",
      "Breed: ", `Dog Breed`, "<br>",
      "Origin: ", Origin, "<br>",
      "Hair Color: ", `Hair Color`, "<br>",
      "Hair Length: ", `Hair Length (cm)`, " cm<br>",
      "Bite Size: ", `Bite Size / Jaw Width (cm)`, " cm"
    ),
    label = ~Name
  )
```

```{css}
/*| echo: false */
.dog-marker-icon {
  border-radius: 50%;
  border: 2px solid white;
  box-shadow: 0 0 4px rgba(0,0,0,0.5);
}
```
